\LARGE \bf Efficient Planar Sample-Based Grasp Planning with Uncertainty Using Multi-Armed Bandit Models [v3 Feb 12, 2015 ]

### 2015-02-11 paper.tex
reduced size, revised bandit section

\title{\LARGE \bf
Efficient Planar Sample-Based Grasp Planning with Uncertainty Using Budgeted Multi-Armed Bandit Models for  [v3 Jan 5, 2015 ] }

@@

\begin{abstract}
\textit{Abstract---}\todo{Not sure if we need to change the authors list or not}Sampling perturbations in shape, state, and control can facilitate grasp planning in the presence of uncertainty arising from noise, occlusions, and surface properties such as transparency and specularities.  Monte-Carlo sampling is computationally demanding, even for planar models. We consider an alternative based on the multi-armed bandit (MAB) model for making sequential decisions, which can apply to a variety of uncertainty models.  We formulate grasp planning as a ``budgeted multi-armed bandit model" (BMAB) with finite stopping time to minimize ``simple regret", the difference between the expected quality of the best grasp and the expected quality of the grasp evaluated at the stopping time.  To evaluate MAB-based sampling, we compare it with Monte-Carlo sampling for grasping an uncertain planar object with shape uncertainty defined by a Gaussian process implicit surface (GPIS), but the method is also applicable to other models of uncertainty.  We derive distributions on contact points, surface normal, and center of mass under shape uncertainty and use these to formulate the associated MAB model, finding that it computes grasps of similar quality to Monte-Carlo sampling and can reduce computation time by an order of magnitude.
\end{abstract}

\begin{abstract}
\textit{Note to Practitioners---}Planning for a grasp in an unknown environment can be difficult due to uncertainties. For example, a given object may have transparency which makes modern kinect-like sensor unable to accurately determine shape or an object may have a built up of mildew or dust, which makes the friction coefficient unknown. Monte-Carlo integration is often used to exhaustively evaluate the distribution on a grasp quality metric given these uncertainties. We apply algorithms from the sequential decision making literature to intelligently allocate samples for grasp quality evaluation to grasps likely to have higher quality given the previous samples, reducing plan time by roughly an order of magnitude.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

     \subfloat{{\includegraphics[width=8cm]{matlab_figures/teaser.eps} }}%

@@

Our main contribution is formulating the problem of ranking a set of candidate grasps according to a quality metric in the presence of uncertainty as a budgeted multi-armed bandit problem. %\todo{Jeff: probably needs to be more specific here, unless we formally describe how to do it in an arbitrary model}.
We study this formulation using probability of force closure~\cite{christopoulos2007handling, weisz2012pose, kehoe2012toward} as a quality metric under uncertainty in pose, shape, robot motion, and friction coefficient. 
We model shape uncertainty using Gaussian process implicit surfaces (GPISs), a Bayesian representation of shape uncertainty that has been used in various robotic applications~\cite{dragiev2011, hollinger2013}. 
Uncertainty in pose is represented as a normal distributions around the orientation and translation of the object.
Uncertainity in motion is represented as a normal distribution around the end point of a planned gripper trajectory and uncertainty in friction coefficient is a normal distribution around an expected friction coefficient.
\todo{Jeff: I personally think the above 3 statements may be too much detail for an intro}
Our approach of using BMAB is applicable to any distributions that can be sampled from, however performance could potentially vary. 
We compare the performance of several popular algorithms for solving the BMAB problem: Bayes UCB, Thompson sampling, and Gittins indices. 
\todo{Going to fill bottom paragraph in later}
Initial results suggest a promising avenue with a Xx improvement over  the traditional Monte-Carlo integration and Xx improvement in the experiments that we tried.

@@

We chose to study our MAB sampling method on distributions for friction coefficient, pose, motion and shape. For shape uncertainty we decided to use a Gaussian process implicit surface representation. Our decision to use this uncertainty model is based on GPIS's ability to combine different modes of noise observations such as tactile, laser and visual~\cite{rasmussen2006, williams2007, dragiev2011} and its recent use in modeling uncertainty for a number of robotic applications.
Hollinger et al. used GPIS as a model of uncertainty to perform active sensing on the hulls in underwater boats \cite{hollinger2013}.
Dragiev et al. showed how GPIS can enable a grasp controller on the continuous signed distance function \cite{dragiev2011}.
Mahler et al. used the GPIS representation to find locally optimal anti-podal grasps by framing grasp planning as an optimization problem \cite{mahler2015gp}.  However, this relied on an approximation to grasp quality without guarantees on accuracy. We propose an adaptive sampling approach known as the Multi-Armed Bandit Model. This paper is a substantially revised and expanded version on \cite{laskey} and \cite{mahler2015gp}.

@@

Uncertainty in object shape results from sensor noise and missing sensor data, which can occur due to transparency, specularity, and occlusions~\cite{mahler2015gp}.
Following ~\cite{laskey2015bandits, mahler2015gp} we represent the distribution over possible surfaces given sensing noise using a Gaussian process implicit surface (GPIS).
A GPIS represents a distribution over signed distance functions (SDFs), a surface representation commonly used in 3D reconstruction and SLAM \cite{}.
A SDF is a real-valued function $f: \mathbb{R}^d \rightarrow \mathbb{R}$ that is greater than 0 outside the object, 0 on the surface and less than 0 inside the object.
A GPIS is a gaussian distribution over SDF values at a fixed set of query points $\mX = \{\bx_1, ... \bx_n\}, \bx_i \in \mathbb{R}^d$, $f(\bx_i) \sim \mN(\mu_{f}(\bx_i),\Sigma_{f}(\bx_i))$, where $\mu_{f}(\cdot)$ and $\Sigma_{f}(\cdot)$ are the mean and covariance functions of the GPIS.
See Appendix A for detail on how to train a mean and covariance function for a GPIS.
In this work, we set $\mX$ to a uniform $M \times M$ grid of points with square cells.
For convenience, in later sections we will refer to the GPIS parameters as $\theta = \left( \mu_{f}(x), \Sigma_{f}(x) \right)$.

\todo{Jeff: Describe alternative representation of shape uncertainty that we run experiments on. Likely this will be Ben's polygonal model}

\subsubsection{Pose Uncertainty}
In typical robotics applications the pose of objects in the envinroment is determined by registering the object frame-of-reference to the control frame-of-reference used for grasp execution.
Therefore pose uncertainty may come from either a) uncertainty about the registration of the robot's grasping frame-of-reference to its sensing frame-of-reference and b) uncertainty about the pose of known object models in the robot's sensor data.
In practice this uncertainty may be quantified based on the algorithms used to register these frames to one another.
The effects of pose uncertainty on robotic grasping has been studied by~\cite{weisz2012pose, kim2012physically}. % cite Ben's RSS workshop paper here

In 2-dimensional space, the pose of an object $T$ is a member of the Lie Algebra $SE(2)$.
This matrix is defined by a rotation angle $\phi$ and two translation coordinates $\bt = (t_x, t_y)$, summarized in parameter vector $\mathbf{\xi} = (\phi, \bt)^T \in \mathbb{R}^3$:

@@

One challenge with pose is that the pose matrix $T$ is used to apply pose perturbations to an object in practice, but uncertainty is mathematically more easily quantified in terms of the pose parameters $\xi$.
Folowing Barfoot and Furgale, we assume that we are given a mean pose matrix $\bar{T} \in SE(3)$ and zero-mean Gaussian uncertainty on the pose parameters $\mathbf{\xi} \sim \mN \left( \mathbf{0}, \Sigma_{\xi} \right)$, and we define the pose random variable $T$ as

\vspace{-2ex}
\begin{align*}
	T  &= \exp \left( \mathbf{\xi}^{\wedge} \right) \bar{T}
\end{align*}

\noindent where $\mathbf{\xi}^\wedge$ is the twist operator as defined in \cite{barfoot2014Pose}.

@@

 \subsubsection{Friction Uncertainty}
As shown in \cite{zheng2005}, uncertainty in friction coefficient can cause grasp quality to significantly vary.
The expected friction coefficient $\hat{\mu}$ could be derived by means of object classification and a look up table~\cite{}.
However, friction coefficients may be uncertain due to factors such as material between a gripper and an object (e.g. dust, water, moisture), variations in the gripper material due to manufacturing tolerances, or misclassification of the object surface to be grasped.
We model uncertainty in friction coefficient as Gaussian noise, $\mu \sim \mN(\hat{\mu},\sigma_{\mu}^2)$.

\subsection{Grasp Quality}\label{sec:grasp_sample}
We measure the quality of grassp using the probability of force closure~\cite{weisz2012pose, kim2012physically, kehoe2012estimating, kehoe2012toward} given a grasp plan $\Gamma$, which we denote $P_F(\Gamma)$.
Force closure measures the ability to resist external wrenches, or force and torques vectors, assuming the grasp can apply infinite force.

Formally, force closure is a binary-valued quantity $F$ that is 1 if a grasp can resist wrenches in arbitrary directions and 0 otherwise.
Let $\mW \in \mathbb{R}^6$ denote the contact wrenches derived from contact locations $\bc_1, ... \bc_m$, normals $\bn_1, .., \bn_m$, friction coefficient $\mu$, and center of mass $\bz$ for a given grasp and shape.
If the origin lies within the convex hull of $\mW$, then the grasp is in force closure\cite{li1988task}.
In this work we rank grasps using the probability of force closure given uncertainty in shape, pose, robot motion, and friction coefficient~\cite{christopoulos2007handling, kehoe2012toward}:
%\vspace{-2ex}
\begin{align*}
	P_F(\Gamma) &= P(F = 1 | \Gamma, \theta, \xi, \rho, \mu).
\end{align*}
\todo{Jeff: revise above symbols for clarity}

@@

Appendix \ref{sec:Appendix}, describes how to draw shape sample from a GPIS model, which is used to compute $p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\xi)$ along with the other sampled distribution on pose ($\xi$) and motion ($\rho$). Appendix \ref{sec:normals}, describes how to sample from $p(\textbf{n}_i|\textbf{c}_i,\theta)$ and presents a novel visualization technique for the distribution on surface normals.  Appendix \ref{sec:mass}, describes a way to calculate the expected center of mass assuming a uniform mass distribution. Then we use these quantities to determine the grasp parameters $g$. Finally, we compute the forces and torques that can be applied by $g$ to form the contact wrench set $\mW$ and evaluate the force closure condition.

@@

\begin{figure}[ht!]
\centering
\includegraphics[width = 6cm, height = 6cm]{figures/Graphical_Model.jpg}
\caption{A graphical model that illustrates the relationship between the different types of uncertainty in an object. Center of Mass uncertainty is dependent on the pose and shape of the object, however friction coefficient is independent of all other types. \todo{Should we use words or symbols for the graphical model?}}
\vspace*{-10pt}
\label{fig:graphical_model}
\end{figure}

@@

\vspace{-2ex}
\begin{align}
\Gamma^* &= \underset{\Gamma \in \mG}{\text{argmax }} P\left( F = 1 | \Gamma, \theta, \xi, \rho, \mu \right) \label{eq:problem_def}
\end{align}

One method to solve Equation ~\ref{eq:problem_def} is to exhaustively evaluate $P_F(\Gamma)$ for all grap plans in $\mG$ using Monte-Carlo integration and then sort the plans by this quality metric.
This method has been evaluated for shape uncertainty~\cite{christopoulos2007handling, kehoe2012estimating} and pose uncertainty~\cite{weisz2012pose} but is computationally expensive since it may require many samples for each of a large set of candidates to converge to the true value.
More recent works have considered adaptive sampling to discard grasp plans that are not likely to be optimal without fully evaluating their quality~\cite{kehoe2012toward} and searching for locally optimal grasp plans over a continuous set using Sequential Convex Programming~\cite{mahler2015opt}.
\todo{Jeff: differentiate from these}
In this work we show that this objective can be framed as a budgeted multi-armed bandit (BMAB) problem.

@@

\subsection{Standard MAB Model}
The multi-armed bandit model, originally described by Robbins \cite{robbins1985some}, is a statistical model of an agent attempting to make a sequence of correct decisions while concurrently gathering information about each possible decision.
Solutions to the multi-armed bandit model have been used in applications for which evaluating all possible options is expensive or impossible, such as the optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.

@@

Success in MAB problems is commonly measured in terms of {\it regret}, the difference between the expected optimal reward and the expected reward of the selected arm on a single pull.
Traditional bandit algorithms minimize cumulative regret, the sum of regret over the entire sequence of arm choices.
Lai and Robbins showed that an optimal solution to the bandit problem is bounded by a logarithmic function of the number of arm pulls~\cite{lai1985asymptotically}.
They presented an algorithm called (Upper Confidence Bound) UCB that obtains this bound asymptotically~\cite{lai1985asymptotically}.
The algorithm maintains a confidence bound on the distribution of reward based on prior observations and pulls the arm with the highest upper confidence bound.
Many variants of UCB have thus been proposed~\cite{}. \todo{Jeff: cite a lot of the literature here}
Since then a several other algorithms have been shown to achieve this bound, such as the Gittins index policy~\cite{} and Thompson sampling for certain reward distributions~\cite{}.

\subsection{Pure Exploration MAB Models}
Our grasp selection problem is similar in that we would like to find the grasp with the highest quality while conserving computational resources.
%Motivated by limited computational resources we allocate sampling resources to efficiently find the best arm.
However, in our problem one only usually cares about the quality when the final grasp is selected for execution ( the difference between the expected quality of the optimal arm and the arm selected is known as ``simple regret'' in the literature) rather than the cumulative regret as studied in the standard MAB problem.
This is an instance of the Pure Exploration multi-armed bandit problem\cite{bubeck2009pure}, in which an agent attempts to recommend the best arm at the end of an exploration phase but is not penalized for making exploratory arm pulls during this phase.
Hence, the exploration and exploitation stage are decoupled. 
The end of the exploration phase, or ``stopping time,'' may not be known to the agent ahead of time.
Therefore, unless otherwise noted, solutions to the Pure Exploration problem are anytime algorithms; they must return a valid solution whenever they are stopped.

Formally, given arms $\lbrace \Gamma_1, ..., \Gamma_K \rbrace$ with respective mean rewards $\mu_1, ..., \mu_K$, the goal in the Pure Exploration problem is to find the optimal arm $\mu^* = \underset{k\in\lbrace 1, ..., K \rbrace}{\mbox{max}} \mu_k$.
The expected simple regret, or suboptimality, at time $t$ is given by
%\vspace{-2ex}
\begin{align}\label{eq:simple_regret}
E[r_t] = \mu^* - \mu_t
\end{align}
\noindent where $\mu_t$ is the estimate of the best arm at time $t$ from the previous observations.

Several recent works have studied Pure Exploration algorithms that lead to upper bounds on the expected regret.
Audibert el al. demonstrated an algorithm called Successive Rejects that divides up the total budget into successively shorter phases and discards the worst arm left at the end of each phase.
This algorithm can return the best arm with near-optimal probability depending on the hardness of the problem and the number of allocated time steps \cite{audibert2010best}, but requires knowledge of the stopping time.
In addition, UCB-like methods have been proposed that measure a confidence gap and then pull the arm with the highest confidence interval \cite{gabillon2012best}.
For example, Bubeck et al. showed that the simple regret at any time for the UCB algorithm is bounded by a polynomial function of the number of timesteps~\cite{bubeck2009pure}.
Several works have showed the relationship between number of timesteps and simple regret for Probably Approximately Correct (PAC) bandit algorithms~\cite{even2006action, mannor2004sample}.
More recently, Bachman and Precup showed that algorithms based on Bayesian posterior sampling outperformed UCB and PAC algorithms in terms of minimizing simple regret~\cite{bachman2013greedy}.
%Even-dar et al. showed that for Probably Approximately Correct (PAC) algorithms, the number of pulls needed to

%Best arm identification has a wide variety of literature that largely falls into two camps: one where the algorithm terminates once a fixed confidence interval around the best arm is met and the Budgeted Multi-Armed Bandit (BMAB) model, in which the algorithm must make a decision at the end of a fixed ``budget'' number of arm pulls.

%\subsection{Fixed Confidence}
%In the fixed confidence setting the forecaster seeks to minimize the simple regret until a fixed confidence threshold is met at which point it terminates. Originally the problem was solved with `racing' algorithms, which used Hoeffding inequalities or the empirical Bernstein inequality to prune arms that were likely to be suboptimal and used uniform allocation to explore the remaining set \cite{maron1993hoeffding} \cite{mnih2008empirical}. These methods were later extended to return the top $m$ arms instead of only the best arm\cite{gabillon2012best}. 
%
%The speed of termination is affected by the hardness of the problem, which relates to the how close the other arms expected reward is to the expected reward top arm in the set \cite{audibert2010best}. In the grasping context this means that achieving a fixed confidence for two similar grasps would require exhaustive sampling from each distribution. 
%
%\subsection{Fixed Budget}
%
%In the Budgeted Multi-Armed Bandit (BMAB) setting the algorithm is given a stopping time and needs to return the current best arm at that stopping time this can be thought of as an anytime algorithm.
%Audibert el al. demonstrated an algorithm called Successive Rejects that divides up the total budget into successively shorter phases and discards the worst arm left at the end of each phase.
%This algorithm can return the best arm with near-optimal probability depending on the hardness of the problem \cite{audibert2010best}.
%In addition, UCB-like methods have been proposed that measure a confidence gap and then pull the arm with the highest confidence interval \cite{gabillon2012best}. For example in \cite{bubeck2009pure}, they showed a link between simple regret and cumulative regret that allowed for the analysis of the existing bandit algorithms like UCB1.

\subsection{Grasp Planning as Pure Exploration}
In this work, we frame the grasp selection problem of \secref{objective} as a Pure Exploration multi-armed bandit problem.
Each arm corresponds to a different grasp plan and pulling an arm corresponds to sampling from the graphical model in Fig. \ref{fig:graphical_model} and evaluating the force closure condition.
Since force closure is a binary value, we can think of each grasp plan $\Gamma_i$ as having a Bernoulli reward distribution with probability of success $P_F(\Gamma_i)$.
Thus, the expected value of the force closure condition for grasp $\Gamma_i$ is $\mu_i = E[F | \Gamma_i, \theta, \xi, \rho, \mu] = P_F(\Gamma_i)$.
Then minimizing the expected simple regret is equivalent to maximizing $P_F$ over the set of candidate grasp plans:

@@

\section{Bayesian Algorithms for MAB}\label{sec:bandit_algorithm}

\todo{Jeff: I find this transition a bit awkward but I'm not sure how to reorg right now. I almost feel like Bayesian methods should come sooner}.
Most of the algorithms discussed in Section~\ref{sec:MAB} are frequentist, meaning the algorithms treat unknown parameters as fixed and use confidence intervals to score the arms. 
In this work, we are particularly interested in Bayesian algorithms that use previous samples to form a belief distribution on the likelihood of achieving force closure \cite{weber1992gittins,agrawal2011analysis}, as these methods have been shown empirically to outperform frequentist algorithms (e.g., UCB) on real datasets such as ad placement~\cite{chapelle2011empirical, bachman2013greedy}.
%However, recently Bayesian approachs have gained interest in the MAB community due to their empirical success on real world problems such as ad suggestions \cite{kaufmann2012bayesian} \cite{agrawal2011analysis}.
%In Bayesian algorithms, the agent maintains a belief distribution over the reward distribution on the arms.

Bayesian algorithms maintain a belief distribution on the grasp quality distributions for each of the candidate grasps to rank.
The belief distribution enables a trade off between exploration and exploitation by increasing confidence around the true reward distribution as more rewards are observed for an arms.
In the case of using force closure $F$ to measure quality, $P_F$ for each candidate grasp is a Bernoulli random variable and the Bayesian conjugate prior is a Beta distribution. 
Beta distributions are specified by shape parameters $\alpha$ and $\beta$, where ($\alpha >0$ and $\beta >0$).
Typically the uniform prior distribution on probability of force closure for each grasp $i$ at time $t = 0$, $\alpha_{i, 0} =1 $ and $\beta_{i, 0} = 1$, would be used used to initialize the algorithm~\cite{}. 
Theoretical results have shown that several algorithms for Beta-Bernoulli reward distributions are capable of achieving the lower bound described by Lai and Robbins~\cite{gittins1983dynamic, agrawal2011analysis, kaufmann2012bayesian}.
%Furthermore in an empirical study Bayesian methods have been shown to outperform the UCB family \cite{chapelle2011empirical}. 
%See \cite{} for a review of bayesian methods in multi-armed bandit problems.

@@

Whats interesting in the context of a Bayesian BMAB problem our graphical model in Fig. \ref{fig:graphical_model}, is now equivalent in terms of inference to \ref{fig:beta_model} and we only need to estimate $\alpha$ and $\beta$ to determine grasp quality. Regardless of the distributions in Fig. \ref{fig:graphical_model}, we are still able to maintain the theoretical guarantees given by the Bayesian MAB algorithms because the probability of force closure is a Beta-Bernoulli Process \cite{agrawal2011analysis} \cite{kaufmann2012bayesian} 
\cite{weber1992gittins}, which we will now discuss for each of the three proposed algorithms in detail. 
\todo{Michael: The above statement is true and I want to convey this message, however it might take some work to convey. Jeff: "We only need to estimate $\alpha$ and $\beta$ to determine grasp quality" is not true. determine -> estimate might fix it}

>>>>

\title{\LARGE \bf
Efficient Planar Sample-Based Grasp Planning with Uncertainty Using Multi-Armed Bandit Models [v3 Feb 12, 2015 ] }

@@

\begin{abstract}
\textit{Abstract---}Sampling perturbations in shape, state, and control can facilitate grasp planning in the presence of uncertainty arising from noise, occlusions, and surface properties such as transparency and specularities.  Monte-Carlo sampling is computationally demanding, even for planar models. We consider an alternative based on the multi-armed bandit (MAB) model for making sequential decisions, which can apply to a variety of uncertainty models.  We formulate grasp planning as a ``budgeted multi-armed bandit model" (BMAB) with finite stopping time to minimize ``simple regret", the difference between the expected quality of the best grasp and the expected quality of the grasp evaluated at the stopping time.  To evaluate MAB-based sampling, we compare it with Monte-Carlo sampling for grasping an uncertain planar object with shape uncertainty defined by a Gaussian process implicit surface (GPIS), but the method is also applicable to other models of uncertainty.  We derive distributions on contact points, surface normal, and center of mass under shape uncertainty and use these to formulate the associated MAB model, finding that it computes grasps of similar quality to Monte-Carlo sampling and can reduce computation time by an order of magnitude.
\end{abstract}

@@

     \subfloat{{\includegraphics[width=8cm]{matlab_figures/pfc.eps} }}%

@@

Our main contribution is formulating the problem of ranking a set of candidate grasps according to a quality metric in the presence of uncertainty as a budgeted multi-armed bandit problem. %\todo{Jeff: probably needs to be more specific here, unless we formally describe how to do it in an arbitrary model}.
We study this formulation using probability of force closure~\cite{christopoulos2007handling, weisz2012pose, kehoe2012toward} as a quality metric under uncertainty in pose, shape, robot motion, and friction coefficient. 
We model shape uncertainty using Gaussian process implicit surfaces (GPISs), a Bayesian representation of shape uncertainty that has been used in various robotic applications~\cite{dragiev2011, hollinger2013}. 
Uncertainty in pose is represented as a normal distributions around the orientation and translation of the object.
Uncertainity in motion is represented as a normal distribution around the end point of a planned gripper trajectory and uncertainty in friction coefficient is a normal distribution around an expected friction coefficient.

Our approach of using BMAB is applicable to any distributions that can be sampled from, however performance could potentially vary. 
We compare the performance of several popular algorithms for solving the BMAB problem: Thompson sampling, and Gittins indices. 
\todo{Going to fill bottom paragraph in later}
Initial results suggest a promising avenue with a Xx improvement over  the traditional Monte-Carlo integration and Xx improvement in the experiments that we tried.

@@

 \todo{Michael: should we include this next section on GPIS}
We chose to study our MAB sampling method on distributions for friction coefficient, pose, motion and shape. For shape uncertainty we decided to use a Gaussian process implicit surface representation. Our decision to use this uncertainty model is based on GPIS's ability to combine different modes of noise observations such as tactile, laser and visual~\cite{rasmussen2006, williams2007, dragiev2011} and its recent use in modeling uncertainty for a number of robotic applications.
Hollinger et al. used GPIS as a model of uncertainty to perform active sensing on the hulls in underwater boats \cite{hollinger2013}.
Dragiev et al. showed how GPIS can enable a grasp controller on the continuous signed distance function \cite{dragiev2011}.
Mahler et al. used the GPIS representation to find locally optimal anti-podal grasps by framing grasp planning as an optimization problem \cite{mahler2015gp}.  However, this relied on an approximation to grasp quality without guarantees on accuracy. We propose an adaptive sampling approach known as the Multi-Armed Bandit Model.

@@

Uncertainty in object shape results from sensor noise and missing sensor data, which can occur due to transparency, specularity, and occlusions~\cite{mahler2015gp}.
Following ~\cite{laskey2015bandits, mahler2015gp} we represent the distribution over possible surfaces given sensing noise using a Gaussian process implicit surface (GPIS).
A GPIS represents a distribution over signed distance functions (SDFs), a surface representation commonly used in 3D reconstruction and SLAM \cite{}.
A SDF is a real-valued function $f: \mathbb{R}^d \rightarrow \mathbb{R}$ that is greater than 0 outside the object, 0 on the surface and less than 0 inside the object.
A GPIS is a gaussian distribution over SDF values at a fixed set of query points $\mX = \{\bx_1, ... \bx_n\}, \bx_i \in \mathbb{R}^d$, $f(\bx_i) \sim \mN(\mu_{f}(\bx_i),\Sigma_{f}(\bx_i))$, where $\mu_{f}(\cdot)$ and $\Sigma_{f}(\cdot)$ are the mean and covariance functions of the GPIS.
See Mahler et al.  for details on how to train a mean and covariance function and sample shapes from a GPIS \cite{mahler2015gp}.
In this work, we set $\mX$ to a uniform $M \times M$ grid of points with square cells.
For convenience, in later sections we will refer to the GPIS parameters as $\theta = \left( \mu_{f}(x), \Sigma_{f}(x) \right)$.

\subsubsection{Pose Uncertainty}
In typical robotics applications the pose of objects in the environment is determined by registering the object frame-of-reference to the control frame-of-reference used for grasp execution.
Therefore pose uncertainty may come from either a) uncertainty about the registration of the robot's grasping frame-of-reference to its sensing frame-of-reference and b) uncertainty about the pose of known object models in the robot's sensor data.
In practice this uncertainty may be quantified based on the algorithms used to register these frames to one another.
The effects of pose uncertainty on robotic grasping has been studied by~\cite{weisz2012pose, kim2012physically}. % cite Ben's RSS workshop paper here

In 2-dimensional space, the pose of an object $T$ is a member of the Lie Group $SE(2)$.
This matrix is defined by a rotation angle $\phi$ and two translation coordinates $\bt = (t_x, t_y)$, summarized in parameter vector $\mathbf{\xi} = (\phi, \bt)^T \in \mathbb{R}^3$:

@@

One challenge with pose is that the pose matrix $T$ is used to apply pose perturbations to an object in practice, but uncertainty is mathematically more easily quantified in terms of the pose parameters $\xi$.
Folowing Barfoot and Furgale, we assume that we are given a mean pose matrix $\bar{T} \in SE(3)$ and zero-mean Gaussian uncertainty on the pose parameters $\mathbf{\xi} \sim \mN \left( \mathbf{0}, \Sigma_{\xi} \right)$. \cite{barfoot2014Pose}.

@@

 \subsubsection{Friction Uncertainty}
As shown in \cite{zheng2005}, uncertainty in friction coefficient can cause grasp quality to significantly vary.
However, friction coefficients may be uncertain due to factors such as material between a gripper and an object (e.g. dust, water, moisture), variations in the gripper material due to manufacturing tolerances, or misclassification of the object surface to be grasped.
We model uncertainty in friction coefficient as Gaussian noise, $\mu \sim \mN(\hat{\mu},\sigma_{\mu}^2)$.

\subsection{Grasp Quality}\label{sec:grasp_sample}
We measure the quality of grasp using the probability of force closure~\cite{weisz2012pose, kim2012physically, kehoe2012estimating, kehoe2012toward} given a grasp plan $\Gamma$, which we denote $P_F(\Gamma)$.
Force closure measures the ability to resist external wrenches, or force and torques vectors, assuming the grasp can apply infinite force.

Formally, force closure is a binary-valued quantity $F$ that is 1 if a grasp can resist wrenches in arbitrary directions and 0 otherwise.
Let $\mW \in \mathbb{R}^6$ denote the contact wrenches derived from contact locations $\bc_1, ... \bc_m$, normals $\bn_1, .., \bn_m$, friction coefficient $\mu$, and center of mass $\bz$ for a given grasp and shape.
If the origin lies within the convex hull of $\mW$, then the grasp is in force closure\cite{li1988task}.
In this work we rank grasps using the probability of force closure given uncertainty in shape, pose, robot motion, and friction coefficient~\cite{christopoulos2007handling, kehoe2012toward}:
%\vspace{-2ex}
\begin{align*}
	P_F(\Gamma) &= P(F = 1 | \Gamma, \theta, \xi, \rho, \mu).
\end{align*}

@@

Mahler et al \cite{mahler2015gp}, describes how to draw shape sample from a GPIS model, which is used to compute $p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\xi)$ along with the other sampled distribution on pose ($\xi$) and motion ($\rho$). We then use these quantities to determine the grasp parameters $g$. Finally, we compute the forces and torques that can be applied by $g$ to form the contact wrench set $\mW$ and evaluate the force closure condition.

@@

\begin{figure}[ht!]
\centering
\includegraphics[width = 6cm, height = 6cm]{figures/Graphical_Model.jpg}
\caption{A graphical model that illustrates the relationship between the different types of uncertainty in an object. Center of Mass uncertainty is dependent on the pose and shape of the object, however friction coefficient is independent of all other types.}
\vspace*{-10pt}
\label{fig:graphical_model}
\end{figure}

@@

\vspace{-2ex}
\begin{align}
\Gamma^* &= \underset{\Gamma \in \mG}{\text{argmax }} P\left( F = 1 | \Gamma, \theta, \xi, \rho, \mu \right) 
\end{align}

Since we only can approximate the probability of force closure, with samples drawn from the distribution $P_F(\Gamma)$ our objective is rewritten as:

\vspace{-2ex}
\begin{align}
\Gamma^* &\approx \underset{\Gamma \in \mG}{\text{argmax }} P\left( F = 1 | \Gamma, \theta, \xi, \rho, \mu \right) \label{eq:problem_def}
\end{align}

One method to solve Equation ~\ref{eq:problem_def} is to exhaustively evaluate $P_F(\Gamma)$ for all grap plans in $\mG$ using Monte-Carlo integration and then sort the plans by this quality metric.
This method has been evaluated for shape uncertainty~\cite{christopoulos2007handling, kehoe2012estimating} and pose uncertainty~\cite{weisz2012pose} but is computationally expensive since it may require many samples for each of a large set of candidates to converge to the true value.
More recent works have considered adaptive sampling to discard grasp plans that are not likely to be optimal without fully evaluating their quality~\cite{kehoe2012toward}. In this work we show that this objective can be framed as a budgeted multi-armed bandit (BMAB) problem, which offers stronger theoretical and empirical performance \cite{agrawal2011analysis}\cite{chapelle2011empirical}.

@@

\subsection{MAB Model}
The multi-armed bandit model, originally described by Robbins \cite{robbins1985some}, is a statistical model of an agent attempting to make a sequence of correct decisions while concurrently gathering information about each possible decision.
Solutions to the multi-armed bandit model have been used in applications for which evaluating all possible options is expensive or impossible, such as the optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.

@@

Success in MAB problems is commonly measured in terms of {\it regret}, the difference between the expected optimal reward and the expected reward of the selected arm on a single pull.
Traditional bandit algorithms minimize cumulative regret, the sum of regret over the entire sequence of arm choices.
Lai and Robbins showed that an optimal solution to the bandit problem is bounded by a logarithmic function of the number of arm pulls~\cite{lai1985asymptotically}.
They presented an algorithm called (Upper Confidence Bound) UCB that obtains this bound asymptotically~\cite{lai1985asymptotically}.
The algorithm maintains a confidence bound on the distribution of reward based on prior observations and pulls the arm with the highest upper confidence bound.
Many variants of UCB have thus been proposed~\cite{cesa2006prediction}. 
Since then a several other algorithms have been shown to achieve this bound, such as the Gittins index policy~\cite{weber1992gittins} and Thompson sampling for certain reward distributions~\cite{agrawal2011analysis}.

\subsection{Grasp Planning as a Multi-Armed Bandit}
In this work, we frame the grasp selection problem of \secref{objective} as a multi-armed bandit problem.
Each arm corresponds to a different grasp plan and pulling an arm corresponds to sampling from the graphical model in Fig. \ref{fig:graphical_model} and evaluating the force closure condition.
Since force closure is a binary value, we can think of each grasp plan $\Gamma_i$ as having a Bernoulli reward distribution with probability of success $P_F(\Gamma_i)$.
Thus, the expected value of the force closure condition for grasp $\Gamma_i$ is $\mu_i = E[F | \Gamma_i, \theta, \xi, \rho, \mu] = P_F(\Gamma_i)$. One can think of the proposed algorithm as an anytime algorithm, because at a unknown stopping time $T_s$, the multi-armed bandit model must return the current highest estimated grasp plan. Minimizing the expected instantaneous regret, the difference quality of grasp chose and the best grasp in the set, at stopping time, $T_s$, is equivalent to maximizing $P_F$ over the set of candidate grasp plans:

@@

\section{Algorithms for MAB}\label{sec:bandit_algorithm}
In this work, we are particularly interested in Bayesian MAB algorithms that use previous samples to form a belief distribution on the likelihood of the parameters specifying the distribution of each arm \cite{weber1992gittins,agrawal2011analysis}, as these methods have been shown empirically to outperform frequentist algorithms (e.g., UCB) on real datasets such as ad placement~\cite{chapelle2011empirical, bachman2013greedy}.
%However, recently Bayesian approachs have gained interest in the MAB community due to their empirical success on real world problems such as ad suggestions \cite{kaufmann2012bayesian} \cite{agrawal2011analysis}.
%In Bayesian algorithms, the agent maintains a belief distribution over the reward distribution on the arms.

Bayesian algorithms maintain a belief distribution on the grasp quality distributions for each of the candidate grasps to rank. In the case of using force closure $F$ to measure quality, $P_F$ for each candidate grasp is a Bernoulli random variable and the Bayesian conjugate prior is a Beta distribution. 
Beta distributions are specified by shape parameters $\alpha$ and $\beta$, where ($\alpha >0$ and $\beta >0$).
Typically the uniform prior distribution on probability of force closure for each grasp $i$ at time $t = 0$, $\alpha_{i, 0} =1 $ and $\beta_{i, 0} = 1$, would be used used to initialize the algorithm~\cite{}. 
Theoretical results have shown that several algorithms for Beta-Bernoulli reward distributions are capable of achieving the lower bound described by Lai and Robbins~\cite{gittins1983dynamic, agrawal2011analysis, kaufmann2012bayesian}.
%Furthermore in an empirical study Bayesian methods have been shown to outperform the UCB family \cite{chapelle2011empirical}. 
%See \cite{} for a review of bayesian methods in multi-armed bandit problems.

@@

Whats interesting in the context of a Bayesian BMAB problem our graphical model in Fig. \ref{fig:graphical_model}, is now equivalent in terms of inference to Fig. \ref{fig:beta_model} and we only need to estimate $\alpha$ and $\beta$ to determine grasp quality. Regardless of the distributions in Fig. \ref{fig:graphical_model}, we are still able to maintain the theoretical guarantees given by the Bayesian MAB algorithms because the probability of force closure is a Beta-Bernoulli Process on the convergence of the solution being near optimal \cite{agrawal2011analysis}
\cite{weber1992gittins} , which we will now discuss for each of the proposed algorithms.
